Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-07 paper/paper.tex
More things

?? Connected, which occurs in many applications
\citep{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,o:EhrlichR11,o:LuoWSN17}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \citep{DBLP:journals/algorithms/AkutsuT13} and trees
\citep{DBLP:conf/mfcs/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the maximum common connected subgraph cannot be deduced from the maximum
common subgraph.

@@

\subsection{The Splitting Algorithm}

@@

\subsection{The $k$-less Subgraph Isomorphism Algorithm}

@@

\subsection{The Clique Encoding}

@@

\begin{figure*}[tb]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups. The $x$-axis is sequential performance and the $y$-axis is 32
    threaded performance, so points below the diagonal line represent a speedup.}
\end{figure*}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-par-t2-vs-clique-par-t4.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t4-vs-clique-par-t8.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-par-t8-vs-clique-par-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t16-vs-clique-par-t32.pdf}

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t2-vs-clique-cilk-t4.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t4-vs-clique-cilk-t8.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t8-vs-clique-cilk-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t16-vs-clique-cilk-t32.pdf}

    \caption{Scalability and reproducibility, clique algorithm, Cilk.}
\end{figure}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}

    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t2-vs-mcsplit-par-t4.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t4-vs-mcsplit-par-t8.pdf}

    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t8-vs-mcsplit-par-t16.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t16-vs-mcsplit-par-t32.pdf}

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure}

>>>>

?? Connected, which occurs in many applications
\citep{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,o:EhrlichR11,o:LuoWSN17}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \citep{DBLP:journals/algorithms/AkutsuT13} and trees
\citep{DBLP:conf/mfcs/DroschinskyKM16}, but the general case remains NP-hard. As illustrated in
\cref{figure:mcsexample}, the maximum common connected subgraph cannot be deduced from the maximum
common subgraph.

@@

\subsection{Domain Splitting}

@@

\subsection{$k$-less Subgraph Isomorphism}

@@

\subsection{Encoding as Maximum Clique}

@@

\begin{figure*}[tb]
    \includegraphics*{gen-graph-as-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33v.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33ved.pdf}

@@

    \includegraphics*{gen-graph-as-plain-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33ve-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-as-sip.pdf}
\end{figure*}

% \begin{figure*}[tb]
%     \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Per-instance speedups. The $x$-axis is sequential performance and the $y$-axis is 32
%     threaded performance, so points below the diagonal line represent a speedup.}
% \end{figure*}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t2-vs-clique-par-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t4-vs-clique-par-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t8-vs-clique-par-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t16-vs-clique-par-t32.pdf}
% 
%     \caption{Scalability and reproducibility, clique algorithm.}
% \end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t2-vs-clique-cilk-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t4-vs-clique-cilk-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t8-vs-clique-cilk-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t16-vs-clique-cilk-t32.pdf}
% 
%     \caption{Scalability and reproducibility, clique algorithm, Cilk.}
% \end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t2-vs-mcsplit-par-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t4-vs-mcsplit-par-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t8-vs-mcsplit-par-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t16-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Scalability and reproducibility, McSplit algorithm.}
% \end{figure}
